Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-03-30 talk/icooolps2011/paper.tex
analyze a bit

For space reasons we cannot perform a full evaluation here, but still want to
present some benchmark numbers. We chose to present two benchmarks, a port of
the classical Richards benchmark in Python and a Python version of the Telco
decimal benchmark\footnote{\texttt{http://speleotrove.com/decimal/telco.html}},
using a pure Python decimal floating point implementation.

@@

XXX analysis

>>>>

For space reasons we cannot perform a full evaluation here, but still want to
present some benchmark numbers. We chose to present two benchmarks, a port of
the classical Richards benchmark in Python and a Python version of the Telco
decimal benchmark\footnote{\texttt{http://speleotrove.com/decimal/telco.html}},
using a pure Python decimal floating point implementation. The results we see in
these two benchmarks seem to repeat themselves in other benchmarks using
object-oriented code, for purely numerical algorithms the speedups are a lot
lower.

@@

Versioned types speed up both benchmarks by a significant factor of around 7.
The speed advantage of maps alones is a lot less clear. Maps also have a memory
advantage which we did not measure here. By themselves, maps improved the
Richards benchmark slightly, but made the Telco benchmark slower. Enabling both
maps and versioned types together yields a significant improvement over just
versioned types for Richards. XXX good explanation. For Telco, enabling both
does not change much.
